---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `targets` package minimal example

[![Launch RStudio Cloud](https://img.shields.io/badge/RStudio-Cloud-blue)](https://rstudio.cloud/project/1430691)

This repository is an example data analysis workflow with [`targets`](https://docs.ropensci.org/targets). The pipeline reads the data from a file, preprocesses it, visualizes it, and fits a regression model. 

## How to access

You can try out this example project as long as you have a browser and an internet connection. [Click here](https://rstudio.cloud/project/1430691) to navigate your browser to an RStudio Cloud instance. Alternatively, you can clone or download this code repository and install the R packages [listed here](https://github.com/wlandau/targets-minimal/blob/03835c2aa4679dcf3f28c623a06d7505b18bee17/DESCRIPTION#L25-L30).

## How to run

1. Open the R console and call `renv::restore()` to install the required R packages.
2. call the [`tar_make()`](https://wlandau.github.io/targets/reference/tar_make.html) function to run the pipeline.
3. Then, call `tar_read(hist)` to retrieve the histogram. 
4. Experiment with [other functions](https://wlandau.github.io/targets/reference/index.html) such as [`tar_visnetwork()`](https://wlandau.github.io/targets/reference/tar_visnetwork.html) to learn how they work.

## File structure

The most important files are:

```{r, eval = FALSE}
├── _targets.R
├── R/
├──── functions.R
├── data/
├──── raw_data.csv
└── index.Rmd
```



```{r}

targets::tar_visnetwork()

```

    * Call `targets::tar_renv(extras = character(0))` to write a `_packages.R` file to expose hidden dependencies.
    * Call `renv::init()` to initialize the `renv` lockfile `renv.lock` or `renv::snapshot()` to update it.
    * Commit `renv.lock` to your Git repository.
